Source Summaries

### 2020-02-23 paper/sourceSummaries/summary4.tex

@@

@@

@@

@@

@@

@@

>>>>

\subsection{{O}n {P}rivacy and {S}ecurity {C}hallenges in {S}mart {C}onnected {H}omes}

@@

\bibentry{bugeja2016privacy}

@@

\noindent
The authors give an overview of the privacy and security challenges directed towards the smart home domain. The authors discuss different constraints, soulution, challenges, and research issues where further investigation is required.

@@

\noindent
Game Theory. The authors identify different attack vectors for smart homes and give some solutions to these attacks.

@@

\noindent
The authors identified different categories of security risks and then listed what a solution would have to look like in order to mitigate the security risks.

@@

\noindent
The authors identified different security risks involved in smart homes. For the devices in smart homes they found problems with resource constraints, lack of user interface, and a need for tamper resistant devices and data. For the communication used in smart homes they found problems with heterogeneous protocols and devices going in and out of the network. The authors also found an issue with devices in smart homes not supporting dynamic patches for various reasons.

@@

\noindent
The authors offer multiple future research directions. They recommend further investigation into, identity management, risk assessment methods, information flow control, and security management methods relating to smart home environments.
